\documentclass[12pt]{article}
\title{Youth Men's Bible Study of FBC Keller: Doctrinal Statement and Guidelines}
\author{Ben Flegel \and Jude Hurst-Bolster \and Lethan Hutchins \and Matthew Kennedy \and Nikolai Burgess }
\date{June 2025}
\begin{document}
\maketitle{}

  This is the official doctrinal statement of the Youth Men's Bible Study of
First Baptist Church of Keller.\footnote{Many items in this document are subject
to change, as this is an early draft.}

  The main goal with this is to grow in our understanding of God by reading and
discussing alongside our brothers in the faith. This will be a time almost
solely devoted to studying and discussing the Word of God in a roundtable
setting.

% \section{Doctrinal Foundations}
%
% \begin{itemize}
%
% 	\item \textbf{First and foremost}, we shall use the Bible as the root of our
% 	doctrinal statement. There is no better resource than the divine Word of
% 	God itself.
%
% 	\item \textbf{Second}, we'll use the Nicene Creed to ensure that all have a clear
% 	understanding of the truth of the gospel.
%
% 	\item \textbf{Third}, we'll use the Athanasian Creed predominantly for
% 	its very clear and descriptive explanation of the triune and divine
% 	nature of God and of the sacrifice of Christ on the cross.
%
% 	\item \textbf{Fourth and finally}, we will use the 1689 London Baptist
% 	Confession of Faith to help train our leaders in basic Baptist doctrinal
% 	truths, as well as for a crash course in church history.
%
% \end{itemize}

\section{Leadership}

\subsection{Who Will Lead?}

  Leadership will be a volunteer position only.

  We would prefer that those who lead be juniors and seniors in high school,
with sophomores being added as voted on by upperclassmen. This way we can ensure
some semblance of maturity within the leadership structure.

  For leadership attributes, we will hold to the teaching of Paul in
1 Timothy\footnote{1 Tim 3:1-13, 4:6-16}, where Paul lists the
qualifications and instructions for those who are in a position of spiritual
leadership.

\subsection{Leadership Resources}

To ensure that all leaders are on the same page, we have a list of resources
that prospective leaders are required to read. That list is as follows:

\begin{itemize}

	% \item The Bible: even though it's obvious, the root of our doctrinal
	% statement is the Bible itself. There is no greater resource than the
	% divine Word of God Himself.

	\item The Nicene Creed

	\item The Athanasian Creed

	\item The 1689 London Baptist Confession of Faith

\end{itemize}

  We also hope to read the next article of the Heidelberg Catechism before we
split into small groups each week.

  The reasoning behind having these resources is twofold:

\begin{itemize}


	\item \textbf{First}, so that we can ensure that all who wish to lead
	have a firm foundation in the truth of the gospel.

	\item \textbf{Second}, so that we can make sure that they know what they
	are getting into.

\end{itemize}

  This is not a position to be taken lightly, as you will be guiding the
discussion; that is to say, not teaching a lesson, but rather making sure that
the conversation stays on track and is at least related to the passage.

\section{Structure, Communication, and Accountability}

\subsection{Basic Structure}

The basic structure is something that we're calling "Bible Study Book Club."

We will have an assigned section of study for that week (anywhere from one to
three chapters, depending on length and content). In the week leading up to the
next meeting, we will spend time studying the passage and taking notes like you
would with any regular Bible study.

When we meet again the following week, we'll come together to have a roundtable
discussion on what we read and compare notes.

\subsection{Scheduling}

\subsection{Communication and Scheduling}

	The method of communication is still up in the air as of the time of
	writing (June 11, 2025), but we still have a few ideas.

	The preferred method is to have the group move to Discord (messaging
	platform with extensive group moderation and organization features) and
	have separate channels (chats within the group) for different topics
	(prayer requests, announcements, etc.)

\subsection{Accountability}

\textbf{Time in the Word}
\begin{itemize}

	\item Reading
	\item Personal Bible study

		% The study for the group should not be a replacement for your own
		% personal time in the Word. Our faith should be our own, and we
		% should have our own personal convictions, but we also need to
		% stay rooted in the Word. By growing in understanding of the
		% Bible through study, we can grow in discernment and in knowledge
		% of the glory of our God.

\end{itemize}

\textbf{Prayer}
\begin{itemize}

	\item Personal prayer life
	\item Prayer requests

\end{itemize}

\textbf{Purity}
\begin{itemize}

	\item Sexual purity
	\item Purity of speech

\end{itemize}

\end{document}
