\documentclass[12pt]{article}
\title{Youth Men's Bible Study of FBC Keller: Doctrinal Statement and Guidelines}
\author{Ben Flegel \and Jude Hurst-Bolster \and Lethan Hutchins \and Matthew
Kennedy \and Nikolai Burgess }
\date{June 2025}
\begin{document}
\maketitle{}

% IF THE GROUP CAUSES DISUNITY OR A DIVIDE WITHIN THE CHURCH, OR IF WE BECOME
% LABELLED AS TOO CALVINIST, THE CHURCH WILL STEP IN AND WE WILL NO LONGER BE
% A GROUP ASSOCIATED WITH THEM.

% Expectations rather than requirements

% Roundtable as the focus

% This is predominately an opportunity to invest in one another through study,
% discussion, and fellowship

  This is the official doctrinal statement of the Youth Men's Bible Study of
First Baptist Church of Keller.\footnote{Many items in this document are subject
to change, as this is an early draft.}

\section{The Goal of the Study}

  Our goal is to uncover the truth of God's Word through study, discussion, and
debate (not arguments, but more of a back and forth between brothers that is
motivated by our mutual appreciation for scripture)

To grow in knowledge and understanding of the Word, and to teach sound doctrine
with brothers in the faith

% Are we just filling our week with Bible study rather than going and doing the
% work of the gospel?

%   The main goal with this is to grow in our understanding of God by reading
% and discussing alongside our brothers in the faith. This will be a time almost
% solely devoted to studying and discussing the Word of God in a roundtable
% setting.

\section{Doctrine}

% Take care that you know what you believe, why you believe it, and that it
% is based solely in sound doctrine as can be found in scripture

% We strive for theological unity

  We also hope to read the next article of the Heidelberg Catechism before we
split into small groups each week.

\subsection{Doctrinal Disagreements}

% Handle disagreements with grace

% Handle disagreements with respect and an open mind

\section{Leadership}

\subsection{Who Will Lead?}

  Leadership will be a volunteer position only.

  We would prefer that those who lead be juniors and seniors in high school,
with sophomores being added as voted on by upperclassmen. This way we can ensure
some semblance of maturity within the leadership structure.

  For leadership attributes, we will hold to the teaching of Paul in
1 Timothy\footnote{1 Tim 3:1-13, 4:6-16}, where Paul lists the
qualifications and instructions for those who are in a position of spiritual
leadership.

\subsection{Leadership Resources}

To ensure that all leaders are on the same page, we have a list of resources
that prospective leaders are required to read. That list is as follows:

% We affirm the Baptist Faith and Message (2000 Revision) and the Covenental
% Statement of First Baptist Church of Keller, Texas.

\begin{itemize}

	\item The Nicene Creed

	\item The Athanasian Creed

	\item The 1689 London Baptist Confession of Faith

% add the BFM2000 and the church covenant???

\end{itemize}

\begin{itemize}

	\item \textbf{First}, so that we can ensure that all who wish to lead
	have a firm foundation in the truth of the gospel.

	\item \textbf{Second}, so that we can make sure that they know what they
	are getting into.

\end{itemize}

  This is not a position to be taken lightly, as you will be guiding the
discussion; that is to say, not teaching a lesson, but rather making sure that
the conversation stays on track and is at least related to the passage.

\section{Structure, Communication, and Accountability}

\subsection{Basic Structure}

	The basic structure is something that we're calling "Bible Study Book Club."

	We will have an assigned section of study for that week (anywhere from one to
three chapters, depending on length and content). In the week leading up to the
next meeting, we will spend time studying the passage and taking notes like you
would with any regular Bible study.

	When we meet again the following week, we'll come together to have a roundtable
discussion on what we read and compare notes.

\subsection{Worship}

\subsection{Scheduling}

\subsection{Communication and Scheduling}

	The method of communication is still up in the air as of the time of
	writing (June 11, 2025), but we still have a few ideas.

	The preferred method is to have the group move to Discord (messaging
	platform with extensive group moderation and organization features) and
	have separate channels (chats within the group) for different topics
	(prayer requests, announcements, etc.)

\subsection{Accountability}

\textbf{Time in the Word}
\begin{itemize}

	\item Reading
	\item Personal Bible study

\end{itemize}

\textbf{Prayer}
\begin{itemize}

	\item Personal prayer life
	\item Prayer requests

\end{itemize}

\textbf{Service}
\begin{itemize}

	\item How have you been serving the church?
	\item How have you been serving outside of the church?
	
\end{itemize}

\textbf{Purity}
\begin{itemize}

	\item Sexual purity
	\item Purity of speech

\end{itemize}

\end{document}
